---
title: "General social survey"
author: "Jacques Taschereau"
date: "`r format(Sys.time(), '%d/%m/%y')`"
output:
  beamer_presentation: default
  pdf_document: default
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE, message=FALSE}
#system("cmd.exe", input = paste('"C:\\Program Files\\R\\R-4.0.4\\bin\\Rscript.exe" C:\\Users\\Razer\\OneDrive\\Documents\\R\\startup.R'))
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
library(foreign)
library(tidyverse)
library(tinytex)
library(data.table)
```

## The general social survey (GSS)

- 6108 columns
- A lot of factors, categorical data
- Will start with the period 1972-2018

- Most of all it contains tons of NA's, which is ok in R




```{r}
#1972 to 2018 gss data
gss <- read.dta("C:/Users/Razer/OneDrive/Documents/R/GSS_stata/GSS7218_R1.dta")

#can change the StringAsFactors value laters
gss <- data.table(gss, key = "id")

#save and load for memory efficiency
save(gss, file = "gss.xdr", compress = FALSE)

load(file = "gss.xdr")

```


## Social surveys

- Other social surveys across the world are compiled

    - Germany: German General Social Survey
    - Canada: Canadian General Social Survey
    - International Social Survey Programme based in Leipzig cumulates those between 58 countries
        - ISSP offers "vintages" on different social topics whenever they cumulate
        
## GSS

- The GSS changed methodology in 2006
- Cross-sectional design to rotating panel design
- Variables now organized into modules

```{r}
#sanity checks
gss %>% 
  filter(year == 2006) %>% 
  select(year, contains("big5"))

gss %>% 
  filter(year >= 2006) %>% 
  select(year, contains("WWWmin"))


#check for key
#id, year combos are unique
key <- tibble(gss) %>% 
  count(id, year) %>% 
  filter(n>1)

```


```{r}
# Mapping the modules to variable names
# This will make the data easily subsettable
# Used https://simplypdf.com/Excel to convert the Panel module identification table
# See https://gss.norc.org/Documents/codebook/Panel%20Codebook.pdf to access the panel codebook

modules <- readxl::read_xlsx("C:/Users/Razer/OneDrive/Documents/R/GSS_stata/Panel Codebook.xlsx")
modules <- data.frame(modules)
modules[,1] <- tolower(modules[,1])

#only convert to tibble to pipe
#we simplify by only keeping the first level module
# modules_1 <- tibble(modules) %>% 
#   select(-Module.II, -Module.III) %>% 
#   group_by(Module.I) %>% 
#   nest()

#storing the gss columns
gss_cols <- (colnames(gss))
gss_cols <- t(t(gss_cols))
gss_cols <- as.data.table(gss_cols)
names(gss_cols)[1] <- "Varname"

#keep all vars in colnames
vars <- left_join(gss_cols, modules, by="Varname")

na.count <- data.table(vars[,1], "na_waves"=rowSums(is.na(vars[,2:4])), "na_modules"=rowSums(is.na(vars[,5:7])))

vars_w_na <- full_join(vars, na.count, by="Varname", keep = F)

vars_keep_top_modules <- tibble(vars_w_na) %>% 
  filter(na_waves <= 1) %>% 
  select(Varname, `Module.I`) %>% 
  group_by(`Module.I`) %>% 
  nest()

#Data entry error!!
#Clergy and sex show 2008 only on the website
#Also shows 34 variables inst of 7

vars %>% 
  filter(`Module.I`=="Clergy/Sex")

vars %>% 
  count(Module.I, Module.II, Module.III) %>% 
  filter(Module.I=="Core")

%>% 
  mutate(Module.Total = rowSums(c(Module.I, Module.II, Module.III)))

# vars_counts <- tibble(vars) %>% 
#   count(`X2006..Panel`,`X2008..Panel`,`X2010..Panel`,`Module.I`,`Module.II`,`Module.III`) %>% 
#   filter((`X2006..Panel`=="X"&&`X2006..Panel`=="X"&&`X2006..Panel`=="X") ||
#          (`X2008..Panel`=="X"&&`X2010..Panel`=="X"))



# tl <- tolower(modules_1$data[[1]]$Varname[1])
# x <- ((gss_cols[,1]==tolower(modules_1$data[[1]]$Varname[1])))
# 
# summary(x)
# length(modules_1$data[[1]]$Varname[])
# str(modules_1$Module.I[1])
# 
# modules_1$data[[1]]$Varname[]
# 
# for(j in 1:length(gss_cols)) {
#   for(i in 1:length(modules_1)) {
#     for (k in 1:length(modules_1$data[[i]]$Varname[])) {
#       if(gss_cols[,1]==tolower(modules_1$data[[i]]$Varname[k])) {
#         gss_cols[j,2] <- modules_1$Module.I[i];
#         k <- k+1;
#       } else {
#         gss_cols[j,2] <- "NULL"
#         k <- k+1;
#       }
#     }
#   }
# }
# 
# modules_1$data[[1]]$Varname[]
# 
# length(colnames(gss))



# for (i in 1:length(modules_1)) {
#   for(j in 1:length(colnames(gss))) {
#   print(modules_1$data[[i]]) 
#   }
# }


```



